Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-10-01 LaTeX_paper/paper.tex
add labeling tool section

>>>>

\section{The Labeling tool}
When the program solves a puzzle it also exports some files that could be used in the future to train
a machine-learning based comparator.
This section is here to explain the data available and the format used.

One piece is uniquely identified by his id piece\_id.
The id is an integer that goes from 0 to Number of pieces - 1.
Each piece has 4 sides that can be identified by the side side\_id,
an integer that goes from 0 to 3.

\subsection{Image of each piece}

Inside the folder results/pieces the program will generate one image
for each one of the pieces of the puzzle. The pieces will be named \{piece\_id\}.jpeg.
An example can be seen in \ref{fig:result_pieces}

\begin{figure}[H]
  \caption{}\label{fig:result_pieces}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/result_pieces.jpeg}
\end{figure}

\subsection{Image of each side}

Inside the folder results/sides the program will generate one image 
for each side of each piece. The images will be named \{piece\_id\}\_\{side\_id\}.jpeg.
An example can be seen in \ref{fig:result_sides}

\begin{figure}[H]
  \caption{}\label{fig:result_sides}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/result_sides.jpeg}
\end{figure}

\subsection{Corners of each piece}
The file corners.json will be generated inside the folder results.
This file will contain a list of pieces.
Each piece has 4 sides, and each side has the coordinates of the two points
that delimit itself.\newline
An example of the generated json can be seen below.

\begin{minipage}{\textwidth}
  \begin{lstlisting}
    [
      {
        "piece_id": 0,
        "side_0": {
          "p1": {"x":955, "y":1924},
          "p2": {"x":1024, "y":1016}
        },
        "side_1": {
          "p1": {"x":1024, "y":1016},
          "p2": {"x":1850, "y":1028}
        },
        "side_2": {
          "p1": {"x":1850, "y":1028},
          "p2": {"x":1814, "y":1992}
        },
        "side_3": {
          "p1": {"x":1814, "y":1992},
          "p2": {"x":955, "y":1924}
        }
      },
      {...},
      {...},
      ...
    ]
  \end{lstlisting}
\end{minipage}

\subsection{Match for each side}
The file connections\_result.json will be generated
inside the folder results. This file will contain a list of pieces,
each piece has 4 sides, and each side has a link to the side of the piece
that matches it. The link can be null if the side is along the border.\newline
An example of the generated json can be seen below.

\begin{minipage}{\textwidth}
  \begin{lstlisting}
    [
      {
        "piece_id": 12,
        "side_0": {
            "piece": 5,
            "side": 0
        },
        "side_1": {
            "piece": 8,
            "side": 0
        },
        "side_2": {
            "piece": 0,
            "side": 0
        },
        "side_3": null
      },
      {...},
      {...},
      ...
    ]

  \end{lstlisting}
\end{minipage}

\section{Conclusions}
In conclusion, this paper's objective can be considered achieved.
It has been documented why real-world puzzles are harder than digital puzzles.
It has also been shown that the same algorithm can have drastically worse
performance when working with real-world puzzles compared to digital ones.

A highly effective labeling tool has also been developed.
It could be used in the future to create a machine learning-based comparator that could significantly
improve the time needed to solve this problem by providing more accurate data.

Even the solver that has been created can be considered a success.
His time complexity is horrible if compared with current state-of-the-art digital puzzle solvers.
But if compared with real world one the algorithm is probably one of the best, if not the best, available online.
